Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes

### 2018-10-07 Ben_Manuscripts/structure_paper/Draft.tex
Added links to code
Updates
comments.

%MRS5: could be punchier. I will keep thinking.  
\title{Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes}
\author{Benjamin J. Coscia}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
\author{Joseph Yelk}
\author{Matthew A. Glaser}
\affiliation{Department of Physics, University of Colorado Boulder, Boulder CO, 80309, USA}
%\author{Richard D. Noble}
\author{Douglas L. Gin}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
\alsoaffiliation{Department of Chemistry and Biochemistry, University of Colorado Boulder, Boulder CO 80309, USA}
\author{Xunda Feng}
\affiliation{Department of Chemical and Environmental Engineering, Yale University, New Haven, Connecticut 06511, USA}
\author{Michael R. Shirts}
\email{michael.shirts@colorado.edu}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
\begin{document}
%MRS13: we might end up adjusting the author list a bit; I will ask Matt where he thinks he and Joe should go.  I will talk to Rich when we get this going; not clear that he actually has contributed.  But that's my job. 
  \graphicspath{{./figures/}}

@@

  Periodic, nanostructured porous polymer membranes made from the cross-linked 
  inverted hexagonal phase
  of self-assembled lyotropic liquid crystals (LLCs) are a promising class of materials
  for selective separations. In this work, we investigated an experimentally
  characterized LLC polymer membrane using atomistic molecular modeling. In particular,
  we compared simulated X-ray diffraction (XRD) patterns with experimental XRD data
  to quantify and understand the differences between simulation and experiment.
  We found that the nanopores are likely composed of 5 columns of stacked LLC monomers
  which surround each hydrophilic core. We learned that these columns likely 
  move independently of each other over time scales that we can not simulate.
  We also found that some of the structure previously attributed to monomer tail 
  tilt is likely instead due to ordered tail packing. Although this system
  has been reported as dry, we show that small amounts of water are necessary
  to fully reproduce all features from the experimental XRD pattern due to
  asymmetries introduced by hydrogen bonds between the monomer head groups and
  water molecules. Finally, we explored the composition and structure of the nanopores
  and reveal that there exists a composition gradient rather than an abrupt
  partition between the hydrophilic and hydrophobic regions. A caveat is
  that the time scales of the dynamics are extremely long for this system, 
  resulting in simulated structures that appear too ordered which requires
  careful examination of the metastable states observed in order to draw any
  conclusions. The clearer picture of the nanoscopic structure of these 
  membranes provided in this study will enable a better understanding of
  the mechanisms of small molecule transport within these nanopores.

  \end{abstract}

@@

  More highly selective nanoporous membranes would be extremely useful in order
  to perform complex aqueous separations with seawater and various sources of
  wastewater. Sodium chloride and boron in seawater
  \cite{fritzmann_state---art_2007}, and organic micropollutants found in
  municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006} are
  examples of the diverse constituents of these water sources. By efficiently
  separating contaminants from feed solutions with highly selective membranes,
  it is possible to reduce the number of required membrane passes and post-treatment steps
  needed for a given filtration process \cite{werber_materials_2016}, thus
  lowering energy requirements. Additionally, one can extract valuable resources
  from the feed streams. For example, flowback water produced during hydraulic
  fracturing of shale formations contains dissolved species such as acetate whose
  extraction has economic value \cite{dischinger_application_2017}.

% More highly selective membranes would be extremely useful for both the
% recovery of valuable dissolved species from and the purification of complex
%  aqueous solutions. The supply of fresh water is being increasingly strained
%  by population growth, industrialization and climate change
%  \cite{elimelech_future_2011}. Consequently, people are turning towards
%  treatment of unconventional water sources such as seawater and wastewater. 
%  In addition to obtaining fresh water from them, these water sources, 
%  particularly municipal and industrial wastewater, have been found to contain 
%  valuable resources which can be separated using highly selective membranes~\cite{sales_resource_2015}.
  % make possible with selectively permeable membranes -- better than thermal distillation

@@

  Reverse osmosis (RO) and nanofiltration (NF) are two prevailing membrane
  filtration processes that can be used to separate solutes on the order of 1 nm
  in size and smaller, as well as ions. However the porous architecture of
  commercially available membranes lack uniformity, which severely impacts their
  selectivity \cite{van_der_bruggen_review_2003}. Although scalable, their
  fabrication involves the spontaneous assembly of polymers into disordered
  structures that offer separation pathways that are tortuous and polydisperse
  in size \cite{werber_materials_2016}. Tortuosity increases the effective
  length that a solute must travel, while pore size polydispersity limits membrane
  selectivity.

@@

  Ordered, nanostructured porous membrane materials have become an increasingly popular
  research area for aqueous separations applications because they offer the 
  ability to control pore architecture at the molecular scale, thereby 
  permitting the design of solute-specific separation membranes 
  \cite{humplik_nanostructured_2011}. However, their development has been 
  limited by the ability to synthesize and scale various technologies. Graphene
  sheets are atomically thick, which results in excellent water permeability but
  defects during manufacturing severely impact selectivity \cite{cohen-tanugi_multilayer_2016}.
  Molecular dynamics (MD) simulations of carbon nanotubes show promise
  \cite{humplik_nanostructured_2011}, but synthetic techniques are unable to
  achieve scalable alignment and pore monodispersity
  \cite{hata_water-assisted_2004,maruyama_growth_2005}. Consequently, there is a
  need for a scalable nanostructured porous membrane.

@@

  Preliminary evidence has shown that cross-linked lyotropic liquid crystal
  (LLC) membranes are scalable and may be capable of performing highly selective
  separations. LLCs are amphiphilic molecules that have the ability to
  self-assemble into porous nanostructures \cite{smith_ordered_1997} and can be
  cross-linked to create mechanically strong membrane films with periodic pores on the
  order of 1 nm in diameter \cite{zhou_supported_2005}. Unlike the pores in most commercial NF
  membranes, polymeric LLC membrane pores are uniform in size because they are
  formed by self-assembly. Since LLC polymer membranes lack an appreciable pore size distribution, they
  inherently exhibit high selectivity due to their strict molecular weight
  cut-off (MWCO)~\cite{zhou_supported_2005}. Additionally, the LLC monomers
  examined in this paper are salts, and therefore lead to Donnan exclusion of
  ions in solution. The membrane gains a net surface charge when counterions from
  the head groups that line the pore walls escape into the feed solution in an
  effort to balance the gradients of concentration and electric potential
  \cite{donnan_theory_1995}.

  The feasibility of nanostructured LLC polymer membranes for selective separations has
  been demonstrated using LLC monomers that form the type 1 bicontinuous cubic
  (Q\textsubscript{I})
  \cite{hatakeyama_water_2011,hatakeyama_nanoporous_2010,carter_glycerol-based_2012},
  and the inverted hexagonal (H\textsubscript{II}) \cite{zhou_supported_2005}
  phases. When separating organic solutes from NaCl, Q\textsubscript{I}-phase
  membrane filtration experiments have shown selectivity 2--3 times higher than
  commercial RO and 6--12 times higher than commercial NF membranes
  \cite{dischinger_application_2017}. When separating a series of various sized
  dyes, the H\textsubscript{II}-phase membrane showed complete rejection of dyes
  bigger than 1.2 nm in size \cite{zhou_supported_2005}.

  The H\textsubscript{II}-phase pore geometry (Figure~\ref{fig:assembly}) has a
  higher theoretical capacity for transport than the Q\textsubscript{I} phase.
  The H\textsubscript{II} phase forms at room temperature in the presence of
  ca.~10 wt\% water and consists of hexagonally packed, hydrophilic pore
  columns\cite{smith_ordered_1997}. In the absence of water, neat monomer will
  form the same hexagonal columnar structure which, in the literature, has been
  referred to as the Col\textsubscript{h} thermotropic
  phase\cite{feng_scalable_2014}. 
  % BJC6: maybe not a necessary detail
%  The most
%  promising Q\textsubscript{I} phase for membrane applications forms at 70\degree
%  C when monomer is mixed with c.a.~20 wt\% glycerol\cite{carter_glycerol-based_2012}.
  Q\textsubscript{I}-phase membranes consist of a tortuous network of three
  dimensionally interconnected pores that prevent optimal through-plane
  transport. In contrast, the densely packed, non-tortuous and uniform sized
  pores of H\textsubscript{II}-phase membranes represent the ideal geometry for
  achieving high solute flux\cite{matyka_tortuosity-porosity_2008}.  However, the
  hexagonally packed LC domains of the H\textsubscript{II}-phase
  generally form mutually unaligned domains,
  which are detrimental to membrane permeability. This domain scale misalignment
  had inhibited further development of this technology, and research efforts
  were focused on the Q\textsubscript{I} phase, whose geometry does not require
  alignment~\cite{zhou_new_2007}.

@@

  However, recently researchers have learned how to macroscopically align the
  hexagonal domains which has revived research into H\textsubscript{II}-phase LLC
  polymer membranes. In 2014, Feng et al.~showed that one can align Col\textsubscript{h}
  domains, created by the ``dry" monomer Na-GA3C11, using a magnetic field
  with subsequent cross-linking to lock the structure in
  place\cite{feng_scalable_2014}. In 2016, Feng et al. showed that one could
  also obtain the same result by confining the neat monomer between PDMS or glass
  substrates since hexagonal mesophases preferentially anchor perpendicular to
  both surfaces\cite{feng_thin_2016}. Current experimental efforts are focused
  on extending the method to the H\textsubscript{II} phase and characterizing
  the performance of these newly aligned systems.

@@

  \begin{figure}
	\centering
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{NaGA3C11.pdf}
		\caption{}~\label{fig:monomer}
	\end{subfigure}
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{monomer_twocolor.pdf}
		\caption{}~\label{fig:atomistic_monomer}
	\end{subfigure}
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{wedge_thick.pdf}
		\caption{}~\label{fig:wedge}
	\end{subfigure}
		\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{columns.pdf}
		\caption{}~\label{fig:wedge_layer}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{hexagonal_packing.pdf}
		\caption{}~\label{fig:hex_packing_simple}
	\end{subfigure}
	\caption{(a) The LLC monomer Na-GA3C11 (b) rendered atomistically (c)
	exhibits wedge-like character. (d) Monomers stack on top of each other to
	create columns with short range order then assemble into pores with  
	hydrophilic head groups (blue) facing towards the pore center. (e) The 
	pores assemble into hexagonally packed columnar mesophases.}~\label{fig:assembly}
  \end{figure}

@@

  Our current understanding of the molecular details of resulting LLC polymer membranes'
  nanostructure is not sufficient to be able to precisely design them for
  specific separations. Dischinger et al. attempted to use an empirical model
  that correlates the physiochemical properties of the counterion used in a 
  Q\textsubscript{I}-phase LLC membrane to solute rejection\cite{dischinger_effect_2017}.
  Although their model showed some qualitative agreement with experiment, the
  quality of fit of their model was limited due to complex solute-membrane 
  interactions that could not easily be modeled. Additionally, they observed
  an unexpected discrepancy in the relationship between uncharged solute
  rejection and water permeability, which will require a more in-depth knowledge of
  the difference between solute and solvent transport.

@@

  %BJC16: This figure could probably be cut or moved to supporting info
  \begin{figure}[!htb]
  \centering
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{cartoon_pore.pdf}
		\caption{}~\label{fig:undetailed_pore}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{detailed_pore.pdf}
		\caption{}~\label{fig:detailed_pore}
	\end{subfigure}
    \caption{(a) Previous understanding of the pores are essentially speculations 
    based on limited chemical and experimental data. (b) We use detailed molecular 
    modeling in this paper in order to appropriately model the pore's complex architecture,
    which is crucial to understanding the mechanism of solute transport. In both 
    pictures, the head group region is colored blue and the tail region is colored cyan.}~\label{fig:detail}
  \end{figure}

  In this paper, we perform molecular modeling of the Col\textsubscript{h}
  thermotropic (i.e., solvent-free) assembly formed by Na-GA3C11. Compared to 
  the lyotropic (i.e, solvent-containing) H\textsubscript{II} phase, the
  Col\textsubscript{h} phase is a simpler starting point. The system is not
  assembled in aqueous phase which allowed us to simulate longer timescales, and
  there exists detailed experimental characterization of the fully aligned state,
  including 2D-WAXS patterns (Figure~\ref{fig:WAXS}) that are useful for 
  reconstructing structural data.

@@

	\item \textit{R-spots}: Within R-alkanes, are four spots of higher
	relative intensity.  Accordingly, we name these reflections R-spots. The
	location of all spots is $\sim\,37^{\circ}$ from the $q_z$ axis in their
	respective quadrants. In many liquid crystal systems one can explain the spots
	as the product of alkane chains tilted with respect to the membrane
	plane\cite{govind_simple_2001}.

	\item \textit{R-pores}: The final feature corresponds to the spacing
	and symmetry of the pore columns. The feature, which we named R-pores,
	is characterized by reflections along the equatorial axis defined by $q_z$ = 0.
	The spacing between dots is indicative of the hexagonal symmetry of the packed
	pores. We observe the same information with higher resolution by looking at the
	same system's 1D-SAXS pattern (Fig.~\ref{fig:SAXS}). The location of the
	leading SAXS peak (closest to $q_r$ = 0) is related to the distance between
	pores.
  \end{enumerate}

  \begin{figure}[!htb]
        \centering
                \begin{subfigure}[t]{0.495\linewidth}
                \centering
                \includegraphics[width=\linewidth]{WAXS_annotated_words.pdf} 
                \caption{}\label{fig:WAXS}
        \end{subfigure}
	\begin{subfigure}[t]{0.405\linewidth}
                \centering
                \includegraphics[width=\textwidth]{SAXS.pdf}
                \caption{}\label{fig:SAXS}
        \end{subfigure}
	\caption{(a) 2D-WAXS gives details about repeating features on the
		order of angstroms. Experimentalists have explained each of the 5 major
		reflections present as follows: (R-$\pi$) Aromatic head groups $\pi-\pi$ stack
		3.7 \AA~apart. (R-double) Monomers arrange vertically in a 2\textsubscript{1}
		helix. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. (R-spots) Monomer
		tails are tilted with respect to the membrane plane. (R-pores) As derived from
		SAXS, the pores are spaced 4.12 nm apart and pack hexagonally (b) (Reproduced
		from \citenum{feng_thin_2016}) The repeat spacing in the 1D-SAXS
		scattering pattern is characteristic of hexagonal packing. The leading peak,
		q*, represents the distance between the d\textsubscript{100} planes. Using this
		distance, we know that the distance between pore centers is 4.12 nm.} 
	\label{fig:SWAXS}
 \end{figure}

@@

  We generated an ensemble of characteristic, low-energy vacuum monomer
  configurations by applying a simulated annealing process to a
  parameterized monomer. We cooled monomers from 1000 K to 50 K over 10
  ns. We randomly pulled a low energy configuration from the
  trajectory then reassigned charges using \texttt{molcharge}. Using the new
  charges, we annealed the monomer system again and pulled a random monomer
  configuration from the trajectory which we used for full system
  construction (Figure~\ref{fig:build_procedure}a). See Section S-\ref{S-section:parameterization} 
  of the Supporting Information for further detail of the parameterization process.

@@

  The timescale for self-assembly of monomers into the hexagonal phase is
  unknown and likely outside of a reasonable length for an atomistic simulation,
  calling for a more efficient way to build the system. Previous work has shown
  a united-atom model self assemble into the H\textsubscript{II} phase
  configuration in $\sim$1000 ns \cite{mondal_self-assembly_2013}.  We
  attempted atomistic self-assembly by packing monomers into a box using Packmol
  \cite{martinez_packmol:_2009}. Simulations of greater than 100 ns show no
  indicators of progress towards an ordered system (see Section S-\ref{S-section:self_assembly} of the 
  Supporting Information). 
  To bypass the slow self-assembly process, we used Python scripts to assemble monomers
  into a structure close to one of a number of hypothesized equilibrium configurations
  (Figure~\ref{fig:build_procedure}).
  %MRS13: Would be nice to say we put the scripts on GitHub.  Additional details about which scripts can be in supporting.
  These initial structures may result in equilibration into slowly-intercoverting
  metastable states, an issue we will address later in the paper.

>>>>

\title{Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes}
\author{Benjamin J. Coscia}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
\author{Joseph Yelk}
\author{Matthew A. Glaser}
\affiliation{Department of Physics, University of Colorado Boulder, Boulder CO, 80309, USA}
%\author{Richard D. Noble}
\author{Douglas L. Gin}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
\alsoaffiliation{Department of Chemistry and Biochemistry, University of Colorado Boulder, Boulder CO 80309, USA}
\author{Xunda Feng}
\affiliation{Department of Chemical and Environmental Engineering, Yale University, New Haven, Connecticut 06511, USA}
\author{Michael R. Shirts}
\email{michael.shirts@colorado.edu}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
\begin{document}
%MRS13: we might end up adjusting the author list a bit; I will ask Matt where he thinks he and Joe should go.  I will talk to Rich when we get this going; not clear that he actually has contributed.  But that's my job. 
  \graphicspath{{./figures/}}

@@

  Periodic, nanostructured porous polymer membranes made from the cross-linked 
  inverted hexagonal phase
  of self-assembled lyotropic liquid crystals (LLCs) are a promising class of materials
  for selective separations. In this work, we investigate an experimentally
  characterized LLC polymer membrane using atomistic molecular modeling. In particular,
  we compare simulated X-ray diffraction (XRD) patterns with experimental XRD data
  to quantify and understand the differences between simulation and experiment.
  We find that the nanopores are likely composed of 5 columns of stacked LLC monomers
  which surround each hydrophilic core. Evidence suggests that these columns likely 
  move independently of each other over longer time scales than accessible via atomistic simulation.
  We also find that WAXS structural features previously attributed to monomer tail 
  tilt is likely instead due to ordered tail packing. Although this system
  has been reported as dry, we show that small amounts of water are necessary
  to reproduce all features from the experimental XRD pattern due to
  asymmetries introduced by hydrogen bonds between the monomer head groups and
  water molecules. Finally, we explore the composition and structure of the nanopores
  and reveal that there exists a composition gradient rather than an abrupt
  partition between the hydrophilic and hydrophobic regions. A caveat is
  that the time scales of the dynamics are extremely long for this system, 
  resulting in simulated structures that appear too ordered, thus requiring
  careful examination of the metastable states observed in order to draw any
  conclusions. The clearer picture of the nanoscopic structure of these 
  membranes provided in this study will enable a better understanding of
  the mechanisms of small molecule transport within these nanopores.

  %MRSF: I changed the description of the ``demonstrating'', ``showing'' verbs to present tense.  The experiments are past tense, but the ``showing'' is present tense, since it is occuring while the reader is reading (like in a presentation - you are showing as they listen).
  \end{abstract}

@@

  More highly selective nanoporous membranes would be extremely useful 
  %in order to perform 
  in performing complex aqueous separations with seawater and various 
  %sources 
  types of
  wastewater. 
  For exaple, 
  Sodium chloride and boron in seawater
  \cite{fritzmann_state---art_2007} and organic micropollutants found in
  municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006} represent just a few of the diverse contaminants 
  of water sources. By efficiently
  separating contaminants from feed solutions with highly selective membranes,
  it is possible to reduce the number of required membrane passes and post-treatment steps
  needed for a given filtration process \cite{werber_materials_2016}, thus
  lowering energy requirements. Additionally, one can also extract valuable resources
  from the feed streams. For example, flowback water produced during hydraulic
  fracturing of shale formations contains dissolved species such as acetate whose
  extraction has economic value \cite{dischinger_application_2017}.

%MRSF: a few selelected edits above, but I think strikes the right balance.
% More highly selective membranes would be extremely useful for both the
% recovery of valuable dissolved species from and the purification of complex
%  aqueous solutions. The supply of fresh water is being increasingly strained
%  by population growth, industrialization and climate change
%  \cite{elimelech_future_2011}. Consequently, people are turning towards
%  treatment of unconventional water sources such as seawater and wastewater. 
%  In addition to obtaining fresh water from them, these water sources, 
%  particularly municipal and industrial wastewater, have been found to contain 
%  valuable resources which can be separated using highly selective membranes~\cite{sales_resource_2015}.
  % make possible with selectively permeable membranes -- better than thermal distillation

@@

  Reverse osmosis (RO) and nanofiltration (NF) are two prevailing membrane
  filtration processes that can be used to separate solutes on the order of 1 nm
  in size and smaller, including 
  %as well as 
  %MRSF: this does seem to blend RO and NF together; is this correct, or are there important differences that should be outlined?
  ions. However, the porous architecture of
  commercially available RO and NF membranes lack uniformity, which severely impacts their
  selectivity \cite{van_der_bruggen_review_2003}. Although scalable, their
  fabrication involves the spontaneous assembly of polymers into disordered
  structures that offer separation pathways that are tortuous and polydisperse
  in size \cite{werber_materials_2016}. Tortuosity increases the effective
  length that a solute must travel, while pore size polydispersity limits membrane
  selectivity.

@@

  Ordered, nanostructured porous membrane materials have become an increasingly popular
  research area for aqueous separations applications because they offer the 
  ability to control pore architecture at the molecular scale, thereby 
  permitting the design of solute-specific separation membranes 
  \cite{humplik_nanostructured_2011}. However, their development has been 
  limited by the ability to synthesize and scale various technologies. Graphene
  sheets are atomically thick, which results in excellent water permeability but
  defects during manufacturing severely impact selectivity \cite{cohen-tanugi_multilayer_2016}.
  Molecular dynamics (MD) simulations of carbon nanotubes have shown promise
  \cite{humplik_nanostructured_2011}, but synthetic techniques are unable to
  achieve scalable alignment and pore monodispersity
  \cite{hata_water-assisted_2004,maruyama_growth_2005}. Consequently, there is a
  need for new materials that could provide scalable nanostructured porous membranes.

@@

  Preliminary evidence has shown that cross-linked lyotropic liquid crystal
  (LLC) membranes can be produced at moderate scale and may be capable of performing highly selective
  separations. LLCs are amphiphilic molecules that have the ability to
  self-assemble into porous nanostructures \cite{smith_ordered_1997} and can be
  cross-linked to create mechanically strong membrane films with periodic pores on the
  order of 1 nm in diameter \cite{zhou_supported_2005}. Unlike the pores in most commercial NF
  membranes, polymeric LLC membrane pores are uniform in size because they are
  formed by self-assembly. Since LLC polymer membranes lack an appreciable pore size distribution, they
  inherently exhibit high selectivity due to their strict molecular weight
  cut-off (MWCO)~\cite{zhou_supported_2005}. Additionally, the LLC monomers
  examined in this paper are salts, and therefore lead to Donnan exclusion of
  ions in solution. The membrane gains a net surface charge when counterions from
  the head groups that line the pore walls escape into the feed solution in an
  effort to balance the gradients of concentration and electric potential
  \cite{donnan_theory_1995}.

  The feasibility of nanostructured LLC polymer membranes for selective separations has
  been demonstrated using LLC monomers that form the type 1 bicontinuous cubic
  (Q\textsubscript{I})
  \cite{hatakeyama_water_2011,hatakeyama_nanoporous_2010,carter_glycerol-based_2012}
  and the inverted hexagonal (H\textsubscript{II}) \cite{zhou_supported_2005}
  phases. When separating organic solutes from NaCl, Q\textsubscript{I}-phase
  membrane filtration experiments have shown selectivity 2--3 times higher than
  commercial RO and 6--12 times higher than commercial NF membranes
  \cite{dischinger_application_2017}. When separating a series of various sized
  dyes, the H\textsubscript{II}-phase membrane showed complete rejection of dyes
  bigger than 1.2 nm in size \cite{zhou_supported_2005}.

  The H\textsubscript{II}-phase pore geometry (Figure~\ref{fig:assembly}) has a
  higher theoretical capacity for transport than the Q\textsubscript{I} phase.
  The H\textsubscript{II} phase forms at room temperature in the presence of
  ca.~10 wt\% water and consists of hexagonally packed, hydrophilic pore
  columns\cite{smith_ordered_1997}. In the absence of water, neat monomer will
  form the same hexagonal columnar structure which, in the literature, has been
  referred to as the Col\textsubscript{h} thermotropic
  phase\cite{feng_scalable_2014}. 
  % BJC6: maybe not a necessary detail
%  The most
%  promising Q\textsubscript{I} phase for membrane applications forms at 70\degree
%  C when monomer is mixed with c.a.~20 wt\% glycerol\cite{carter_glycerol-based_2012}.
  Q\textsubscript{I}-phase membranes consist of a tortuous network of three
  dimensionally interconnected pores that prevent optimal through-plane
  transport. In contrast, the densely packed, non-tortuous and uniform sized
  pores of H\textsubscript{II}-phase membranes represent the ideal geometry for
  achieving high solute flux\cite{matyka_tortuosity-porosity_2008}.  However, the
  hexagonally packed LC domains of the H\textsubscript{II}-phase
  generally form mutually unaligned domains, which 
  %are detrimental to 
  hurts
  membrane permeability. This domain scale misalignment
  had inhibited further development of this technology, and research efforts
  were focused on the Q\textsubscript{I} phase, whose geometry does not require
  alignment~\cite{zhou_new_2007}.

@@

  However, recently researchers have learned how to macroscopically align the
  hexagonal domains which has revived research into H\textsubscript{II}-phase LLC
  polymer membranes. In 2014, Feng et al.~showed that one can align Col\textsubscript{h}
  domains, created by the ``dry" monomer Na-GA3C11, using a magnetic field
  with subsequent cross-linking to lock the structure in
  place\cite{feng_scalable_2014}. In 2016, Feng et al.~showed that one could
  also obtain the same result by confining the neat monomer between PDMS or glass
  substrates since hexagonal mesophases preferentially anchor perpendicular to
  both surfaces\cite{feng_thin_2016}. Current experimental efforts are focused
  on extending the method to the H\textsubscript{II} phase and characterizing
  the performance of these newly aligned systems.

@@

  \begin{figure}
	\centering
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{NaGA3C11.pdf}
		\caption{}~\label{fig:monomer}
	\end{subfigure}
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{monomer_twocolor.pdf}
		\caption{}~\label{fig:atomistic_monomer}
	\end{subfigure}
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{wedge_thick.pdf}
		\caption{}~\label{fig:wedge}
	\end{subfigure}
		\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{columns.pdf}
		\caption{}~\label{fig:wedge_layer}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{hexagonal_packing.pdf}
		\caption{}~\label{fig:hex_packing_simple}
	\end{subfigure}
        %MRSF: in the actual paper, there would only be room for about a half-page figure, max.  Can hyou reduce the especially the c/d/e sizes so that it fully fits in a half-page figure? 
	\caption{(a) The LLC monomer Na-GA3C11 (b) rendered atomistically (c)
	exhibits wedge-like character. (d) Monomers stack on top of each other to
	create columns with short range order then assemble into pores with  
	hydrophilic head groups (blue) facing towards the pore center. (e) The 
	pores assemble into hexagonally packed columnar mesophases.}~\label{fig:assembly}
  \end{figure}

@@

  Our current understanding of the molecular details of resulting LLC polymer membranes'
  nanostructure is not sufficient to be able to precisely design them for
  specific separations. Dischinger et al.~attempted to use an empirical model
  that correlates the physiochemical properties of the counterion used in a 
  Q\textsubscript{I}-phase LLC membrane to solute rejection\cite{dischinger_effect_2017}.
  Although their model showed some qualitative agreement with experiment, the
  quality of fit of their model was limited due to complex solute-membrane 
  interactions that could not easily be modeled. Additionally, they observed
  an unexpected discrepancy in the relationship between uncharged solute
  rejection and water permeability, which will require a more in-depth knowledge of
  the difference between solute and solvent transport.

@@

  %BJC16: This figure could probably be cut or moved to supporting info
  \begin{figure}[!htb]
  \centering
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{cartoon_pore.pdf}
		\caption{}~\label{fig:undetailed_pore}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{detailed_pore.pdf}
		\caption{}~\label{fig:detailed_pore}
	\end{subfigure}
    %MRSF: will probably need smaller figures for the paper. 
    \caption{(a) Previous understanding of the pores are essentially speculations 
    based on limited chemical and experimental data. (b) We use detailed molecular 
    modeling in this paper in order to appropriately model the pore's complex architecture,
    which is crucial to understanding the mechanism of solute transport. In both 
    pictures, the head group region is colored blue and the tail region is colored cyan.}~\label{fig:detail}
  \end{figure}

  In this paper, we perform molecular modeling of the Col\textsubscript{h}
  thermotropic (i.e., solvent-free) assembly formed by Na-GA3C11. Compared to 
  the lyotropic (i.e, solvent-containing) H\textsubscript{II} phase, the
  Col\textsubscript{h} phase is a simpler starting point. The system is not
  assembled in aqueous phase which allowed us to simulate longer timescales
  by omitting the solvent in the simulations,
  and there exists detailed experimental characterization of the fully aligned state,
  including 2D-WAXS patterns (Figure~\ref{fig:WAXS}) that are useful for 
  reconstructing structural data.

@@

	\item \textit{R-spots}: Within R-alkanes, are four spots of higher
	relative intensity.  Accordingly, we name these reflections R-spots. The
	location of all spots is $\sim$$37^{\circ}$ from the $q_z$ axis in their
	respective quadrants. In many liquid crystal systems, such spots are explaioned
	as the result of alkane chains tilted with respect to the membrane
	plane\cite{govind_simple_2001}.

	\item \textit{R-pores}: The final significant feature corresponds to the spacing
	and symmetry of the pore columns. The feature, which we named R-pores,
	is characterized by reflections along the equatorial axis defined by $q_z$ = 0.
	The spacing between dots is indicative of the hexagonal symmetry of the packed
	pores. We observe the same information with higher resolution by looking at the
	same system's 1D-SAXS pattern (Fig.~\ref{fig:SAXS}). The location of the
	leading SAXS peak (closest to $q_r$ = 0) is related to the distance between
	pores.
  \end{enumerate}

  \begin{figure}[!htb]
        \centering
                \begin{subfigure}[t]{0.495\linewidth}
                \centering
                \includegraphics[width=\linewidth]{WAXS_annotated_words.pdf} 
                \caption{}\label{fig:WAXS}
        \end{subfigure}
	\begin{subfigure}[t]{0.405\linewidth}
                \centering
                \includegraphics[width=\textwidth]{SAXS.pdf}
                \caption{}\label{fig:SAXS}
        \end{subfigure}
	\caption{(a) 2D-WAXS gives details about repeating features on the
		order of angstroms. Experimentalists have explained each of the 5 major
		reflections present as follows: (R-$\pi$) Aromatic head groups $\pi-\pi$ stack
		3.7 \AA~apart. (R-double) Monomers arrange vertically in a 2\textsubscript{1}
		helix. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. (R-spots) Monomer
		tails are tilted with respect to the membrane plane. (R-pores) As derived from
		SAXS, the pores are spaced 4.12 nm apart and pack hexagonally (b) (Reproduced
		from Ref.\citenum{feng_thin_2016}) The repeat spacing in the 1D-SAXS
		scattering pattern is characteristic of hexagonal packing. The leading peak,
		q*, represents the distance between the d\textsubscript{100} planes, which translates 
                into a distance between pore centers of 4.12 nm.} 
	\label{fig:SWAXS}
 \end{figure}

@@

  We generated an ensemble of characteristic, low-energy vacuum monomer
  configurations by applying a simulated annealing process to a
  parameterized monomer. We cooled monomers from 1000 K to 50 K over 10
  ns. We randomly pulled a low energy configuration from the
  trajectory then reassigned charges using \texttt{molcharge}. Using the new
  charges, we annealed the monomer system again and pulled a random monomer
  configuration from the trajectory which we used for full system
  construction (Figure~\ref{fig:build_procedure}a). Section S-\ref{S-section:parameterization} 
  of the Supporting Information provides further detail of the parameterization process.

@@

  The time scale for self-assembly of monomers into the hexagonal phase is
  unknown and likely outside of a reasonable length for an atomistic simulation,
  requiring a more efficient way to build the system. Previous work has shown
  a united-atom model of LLC can self-assemble into the H\textsubscript{II} phase
  configuration in $\sim$1000 ns \cite{mondal_self-assembly_2013}.  We
  attempted atomistic self-assembly by packing monomers into a box using Packmol
  \cite{martinez_packmol:_2009}. Simulations of greater than 100 ns show no
  indicators of progress towards an ordered system (see Section S-\ref{S-section:self_assembly} of the 
  Supporting Information). 
  To bypass the slow self-assembly process, we used a variety of automated procedures 
  %MRSF: code language is not as important
  %Python scripts 
  to assemble monomers
  into a structure close to one of a number of hypothesized equilibrium configurations
  (Figure~\ref{fig:build_procedure}).
  %MRSF: where's the reference for the build scripts repository?
  %MRS13: Would be nice to say we put the scripts on GitHub.  Additional details about which scripts can be in supporting.
  These initial structures may result in equilibration into slowly-intercoverting
  metastable states, an issue we will address later in the paper.
